---
title: "Exercises [Part 1]"
output: 
  html_document:
    theme: flatly
---

```{r include = F}
library(bupaR)
library(bupaRtutorial)
```

In this exercise we will be looking at an event log containing recorded eating activities of a group of people. The eventlog has the name `eating_patterns` and can be seen below. Each case is a person and each activity instance is a meal.


```{r}
eating_patterns
```

Try to find the answer to the following questions. The first one has been solved for you as an example.


1. How many different persons are there in the data?

```{r}
n_cases(eating_patterns)
```

2. How many different types of activities were recorded?

```{r}
# Your code goes here:

```

3. How many meals or preparation activities were recorded?

```{r}


```

4. What is the time frame of the data? I.e. when was the data recorded? (Hint: try the `summary` function).

```{r}



```

5. What is the most common activity? 

```{r}




```

6. Does this event log contain resources? Please check.

```{r}




```

7. The "processing time" is a the time a person spends on a certain activity. This can be computed as follows for activities.

The `processing_time` function is called a metric, of which we will see more examples later. Have a look at the code below, and it's output. Can you see which of the activities (on average) took the most time?

```{r}
processing_time(eating_patterns, level = "activity", units = "hours")
```

8. We would like to know the processing time for each case: in other words, which of the persons spends the most time preparing and eating his meals? And which the least?

Copy the code above, and change the level argument to "case". Can you find the answer to the question?

```{r}



```





